Context-dependent consequences of including lagged effects in demographic models

### 2022-05-06 docs/paper.Rmd
one line per sentence
sketch out some plots

```{r lambdas, results='asis'}
pandoc.table(
  tar_read(lambda_table),
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right", "right", "right", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambda) Population growth rates for continuous forest (cf) and forest fragments (ff) under different kinds of IPMs with bootstrapped 95% confidence intervals."
)

@@

```{r}
#| example-figure,
#| fig.cap = "A caption for an example figure. It can be long and span mutiple
#|   lines like this."
plot(cars)
```

>>>>

```{r lambdas, results='asis'}
pandoc.table(
  tar_read(lambda_table),
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right", "right", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambda) Population growth rates for continuous forest (cf) and forest fragments (ff) under different kinds of IPMs with bootstrapped 95% confidence intervals."
)

@@

```{r}
#| pva,
#| fig.cap = "Population trajectories for all three IPMs in both habitats"
tar_load(c(
  ipm_det_cf,
  ipm_det_ff,
  ipm_stoch_cf,
  ipm_stoch_ff,
  ipm_dlnm_cf,
  ipm_dlnm_ff
))

ipm_list <- 
  list(det_cf = ipm_det_cf,
       det_ff = ipm_det_ff,
       stoch_cf = ipm_stoch_cf,
       stoch_ff = ipm_stoch_ff,
       dlnm_cf = ipm_dlnm_cf,
       dlnm_ff = ipm_dlnm_ff)

plot_df <- 
  ipm_list %>% map_df(~{
  pop_states <- pop_state(.x)

    lapply(pop_states, colSums) %>%
    as_tibble() %>% 
    mutate(n = n_log_size + n_sdlg,
           t = 1:n())
}, .id = "model") %>% 
  separate(model, into = c("ipm", "habitat"))

ggplot(plot_df, aes(x = t, y = n, color = habitat)) +
  geom_line() +
  facet_wrap(~ipm,ncol = 1)
```
